---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vmeasur

<!-- badges: start -->
<!-- badges: end -->

The goal of vmeasur is to quantify the contractile nature of vessels monitored under an operating microscope.

## Installation

You can install the released version of vmeasur from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("vmeasur")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JamesHucklesby/vmeasur")
```
## Calibrating the operating microscope

To calibrate an operating microscope, take an image of a gradiated ruler. You can then use
this function to calculate the number of pixels per mm.

```r 
calibrate_pixel_size()
```

## Measuring the vessel diameter

Once video data is collected, the region of interest can be selected using select_roi. This
provides a wizard that will assist the user through image analysis.

```r
select_roi()
```

Once selected, vmeasur can output a variety of important parameters and graphs

```{r pressure, echo = FALSE}
library(vmeasur)
mean = quantify_mean_width(example_vessel)
mean[[1]]
head(mean[[2]])
head(mean[[3]])
head(mean[[4]])

width_position = quantify_width_position(example_vessel)
width_position[[1]]
width_position[[2]]

mean_sections = quantify_mean_width_sections(example_vessel)
mean_sections[[1]]
mean_sections[[2]]
mean_sections[[3]]
mean_sections[[4]]
head(mean_sections[[5]])
head(mean_sections[[6]])

```

